---
title: "ECDC COVID-19"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    social: menu
runtime: shiny
---

```{r setup, include=FALSE}

#------------------ Packages ------------------

library(ggplot2)
library(hrbrthemes)
library(shinydashboard)
library(shiny)
library(lubridate)
library(scales)
library(plotly)
library(knitr)
library(dplyr)
library(DT)

#------------------ Data ------------------

source("01.Get_data.R")

#------------------ Parameters ------------------

confirmed_color <- "#000080"
main_color <- "#000000"
death_color <- "#000080"

#------------------ Data ------------------

colnames(data) <- c("Date","Day","Month","Year","Cases","Deaths","Country","GeoId","TerritoryCode","PopData2018")

# Only select countries with more than 100 cases

Aux <- data %>% group_by(Country) %>% mutate(CumSum = cumsum(Cases))
Aux <- Aux %>% filter(CumSum>100)
Countries <- unique(Aux$Country)
DfCountries <- data.frame(Countries=Countries,Id=c(1:length(Countries)))
ListCountries <- as.list(DfCountries$Id)
names(ListCountries) <- DfCountries$Countries

#------------------ Last update ------------------

data$Date <- as.Date(data$Date, format="%d/%m/%Y")
LastUpdate <- max(data$Date)

whichspain <- as.numeric(ListCountries['Spain'])

```

<!-- <style>                      -->
<!-- .navbar { -->
<!--   border-color:black; -->
<!--   color:black!important; -->
<!-- } -->
<!-- </style> -->

Summary
=======================================================================

Input {.sidebar}
-----------------------------------------------------------------------

```{r}

# SelectInput

selectInput("CountryId", label = h3("Select country"), 
  choices = ListCountries,
  selected = whichspain)

```

```{r}

# Get data

df1 <- eventReactive(input$CountryId,{
  
# Selected country
  
SelectedCountry <- as.character(DfCountries$Countries[as.integer(input$CountryId)])

# Filter and mutate

df0 <- data %>%
  arrange(Date) %>% 
  filter(Country == SelectedCountry) %>%
  mutate(CumCases = cumsum(Cases),
         CumDeaths = cumsum(Deaths),
         LogCases = log(Cases),
         LogDeaths = log(Deaths),
         CumLogCases = log(CumCases),
         CumLogDeaths = log(CumCases)) %>%
  filter(CumCases > 100)

# Day Index

df0 <- df0 %>% mutate(DayIndex = c(1:nrow(df0)))

# Move log(0) to 0

df0 <- df0 %>% mutate(LogCases = ifelse(LogCases<0,0,LogCases),
                      LogDeaths = ifelse(LogDeaths<0,0,LogDeaths),
                      CumLogCases = ifelse(CumLogCases<0,0,CumLogCases),
                      CumLogDeaths = ifelse(CumLogDeaths<0,0,CumLogDeaths))

# Output

df0

})

```

`r hr()`

`r paste0("Last update:", " ",LastUpdate)`

`r hr()`

The 2019–20 coronavirus pandemic is an ongoing pandemic of coronavirus disease 2019 (COVID-19), caused by severe acute respiratory syndrome coronavirus 2 (SARS-CoV-2). 

`r hr()`

The outbreak was first identified in Wuhan, Hubei, China, in December 2019. The World Health Organization (WHO) declared the outbreak to be a Public Health Emergency of International Concern on 30 January 2020 and recognized it as a pandemic on 11 March.

`r hr()`

The source of the data is the ECDC (European Centre for Disease Prevention and Control), an European Agency. They update the database once a day.

`r hr()`

Data shown here is from countries with more than 100 confirmed cases. Plots also start after the 100th confirmed case.

`r hr()`

More information in **about**

`r hr()`

`r helpText("Developed by ",a("Ignasi Pascual", href = "https://github.com/ipveka"),style = "padding-left:1em; padding-right:1em;position:absolute;")`

Row
-----------------------------------------------------------------------

### Confirmed {.value-box}

```{r}

flexdashboard::renderValueBox({

flexdashboard::valueBox(value = paste(format(max(df1()$CumCases), big.mark = "."), "", sep = " "), 
         caption = "Total Confirmed Cases", 
         color = confirmed_color)
  
})

```

### Deaths {.value-box}

```{r}


flexdashboard::renderValueBox({

flexdashboard::valueBox(value = paste(format(sum(df1()$Deaths), big.mark = "."), "", sep = " "), 
         caption = "Death Cases",
         color = death_color)
})

```

Row
-----------------------------------------------------------------------

### Cases per day 

```{r}

# Call

renderPlotly({

# Ggplot2

p1 <- ggplot(data = df1(), aes(x = Date, y = Cases)) + theme_light() + 
      geom_line(color = main_color) + labs(x = "Time", y = "Cases", title = "Reported cases per day") +
      theme(panel.grid.major.y = element_blank(),panel.grid.minor.y = element_blank()) +
      scale_x_date(expand = c(0,0), date_breaks = "1 week", date_labels = "%b %d")

ggplotly(p1)

})

```

### Deaths per day
    
```{r}

# Call

renderPlotly({

# Ggplot2

p2 <- ggplot(data = df1(), aes(x = Date, y = Deaths)) + theme_light() + 
      geom_line(color = main_color) + labs(x = "Time", y = "Deaths", title = "Reported deaths per day") +
      theme(panel.grid.major.y = element_blank(),panel.grid.minor.y = element_blank()) +
      scale_x_date(expand = c(0,0), date_breaks = "1 week", date_labels = "%b %d")

ggplotly(p2)

})

```

Row
-----------------------------------------------------------------------

### Cumulative cases per day 

```{r}

# Call

renderPlotly({

# Ggplot2

p3 <- ggplot(data = df1(), aes(x = Date, y = CumCases)) + theme_light() + 
      geom_line(color = main_color) + labs(x = "Time", y = "Cases", title = "Reported cumulative cases") +
      theme(panel.grid.major.y = element_blank(),panel.grid.minor.y = element_blank()) +
      scale_x_date(expand = c(0,0), date_breaks = "1 week", date_labels = "%b %d")

ggplotly(p3)

})

```

### Cumulative deaths per day
    
```{r}

# Call

renderPlotly({

# Ggplot2

p4 <- ggplot(data = df1(), aes(x = Date, y = CumDeaths)) + theme_light() + 
      geom_line(color = main_color) + labs(x = "Time", y = "Deaths", title = "Reported cumulative deaths") +
      theme(panel.grid.major.y = element_blank(),panel.grid.minor.y = element_blank()) +
      scale_x_date(expand = c(0,0), date_breaks = "1 week", date_labels = "%b %d")

ggplotly(p4)

})

```

Logarithmic
=======================================================================

Row
-----------------------------------------------------------------------

### Confirmed {.value-box}

```{r}

flexdashboard::renderValueBox({

flexdashboard::valueBox(value = paste(format(max(df1()$CumCases), big.mark = "."), "", sep = " "), 
         caption = "Total Confirmed Cases", 
         color = confirmed_color)
  
})

```

### Deaths {.value-box}

```{r}


flexdashboard::renderValueBox({

flexdashboard::valueBox(value = paste(format(sum(df1()$Deaths), big.mark = "."), "", sep = " "), 
         caption = "Death Cases",
         color = death_color)
})

```

Row
-----------------------------------------------------------------------

### Log-Cases per day 

```{r}

# Call

renderPlotly({

# Ggplot2

p5 <- ggplot(data = df1(), aes(x = Date, y = LogCases)) + theme_light() + 
      geom_line(color = main_color) + labs(x = "Time", y = "Cases", title = "Reported cases per day") +
      theme(panel.grid.major.y = element_blank(),panel.grid.minor.y = element_blank()) +
      scale_x_date(expand = c(0,0), date_breaks = "1 week", date_labels = "%b %d")

ggplotly(p5)

})

```

### Log-Deaths per day
    
```{r}

# Call

renderPlotly({

# Ggplot2

p6 <- ggplot(data = df1(), aes(x = Date, y = LogDeaths)) + theme_light() + 
      geom_line(color = main_color) + labs(x = "Time", y = "Deaths", title = "Reported deaths per day") +
      theme(panel.grid.major.y = element_blank(),panel.grid.minor.y = element_blank()) +
      scale_x_date(expand = c(0,0), date_breaks = "1 week", date_labels = "%b %d")

ggplotly(p6)

})

```

Row
-----------------------------------------------------------------------

### Log-Cumulative cases per day 

```{r}

# Call

renderPlotly({

# Ggplot2

p7 <- ggplot(data = df1(), aes(x = Date, y = CumLogCases)) + theme_light() + 
      geom_line(color = main_color) + labs(x = "Time", y = "Cases", title = "Reported cumulative cases") +
      theme(panel.grid.major.y = element_blank(),panel.grid.minor.y = element_blank()) +
      scale_x_date(expand = c(0,0), date_breaks = "1 week", date_labels = "%b %d")

ggplotly(p7)

})

```

### Log-Cumulative deaths per day
    
```{r}

# Call

renderPlotly({

# Ggplot2

p8 <- ggplot(data = df1(), aes(x = Date, y = CumLogDeaths)) + theme_light() + 
      geom_line(color = main_color) + labs(x = "Time", y = "Deaths", title = "Reported cumulative deaths") +
      theme(panel.grid.major.y = element_blank(),panel.grid.minor.y = element_blank()) +
      scale_x_date(expand = c(0,0), date_breaks = "1 week", date_labels = "%b %d")

ggplotly(p8)

})

```

Data
=======================================================================

```{r}

renderDataTable({

datatable(df1(),
  options = list(
  columnDefs = list(list(className = 'dt-center', targets = 5)),
  pageLength = 20,
  lengthMenu = c(5, 10, 15, 20),
  scrollX='400px'
))
  
})

```

About
=======================================================================

**Information**

`r paste0("Last update:", " ",LastUpdate)`

`r hr()`

**General**

The 2019–20 coronavirus pandemic is an ongoing pandemic of coronavirus disease 2019 (COVID-19), caused by severe acute respiratory syndrome coronavirus 2 (SARS-CoV-2). 

The outbreak was first identified in Wuhan, Hubei, China, in December 2019. The World Health Organization (WHO) declared the outbreak to be a Public Health Emergency of International Concern on 30 January 2020 and recognized it as a pandemic on 11 March.

The source of the data is the ECDC (European Centre for Disease Prevention and Control), an European Agency. They update the database once a day.

`r hr()`

**Data**

Health authorities: **https://www.who.int/**

Covid-19 Info: **https://en.wikipedia.org/wiki/2019%E2%80%9320_coronavirus_pandemic**

Data source: **https://www.ecdc.europa.eu/en/publications-data/download-todays-data-geographic-distribution-covid-19-cases-worldwide**

The agency: **https://www.ecdc.europa.eu/en/about-us/ecdcs-organisational-structure**

`r hr()`

**Notes**

Plots in Summary start from the day there were 100 active cases. 

`r hr()`

**Packages**

* Dashboard interface - the [flexdashboard](https://rmarkdown.rstudio.com/flexdashboard/) package
* Visualization - the [ggplot2] (https://ggplot2.tidyverse.org/) package
* Tables - the [DT](https://rstudio.github.io/DT/) package

`r hr()`

**Deployment and reproducibly**

The dashboard was deployed to Github docs. If you wish to deploy and/or modify the dashboard on your Github account, you can apply the following steps:

* Fork the dashboard [repository](https://github.com/ipveka/ECDC_Dashboard_Covid19), or
* Clone it and push it to your Github package

`r hr()`

`r helpText("Developed by ",a("Ignasi Pascual", href = "https://github.com/ipveka"),style = "padding-left:1em; padding-right:1em;position:absolute;")`
